\documentclass[12pt, titlepage]{article}

% Imported Packages
%------------------------------------------------------------------------------
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{extarrows}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage[round]{natbib}
\usepackage{hyperref}
\usepackage{soul}

%------------------------------------------------------------------------------

% Header and Footer
%------------------------------------------------------------------------------
\pagestyle{plain}  
\renewcommand\headrulewidth{0.4pt}                          
\renewcommand\footrulewidth{0.4pt}                                    
%------------------------------------------------------------------------------

% Title Details
%------------------------------------------------------------------------------
\title{SE 4GB6: Final Demo Contract\\ The Cut}
\author{Group 17
		\\ Joseph Lu - luy89
		\\ Matthew Po - pom
		\\ Stanley Liu - liuz23
		\\ Suhavi Sandhu - sandhs11
}
\date{November 16, 2019}                            
%------------------------------------------------------------------------------

% Document
%------------------------------------------------------------------------------
\begin{document}

\maketitle	
\newpage

\section{Contract}
% Begin Section
    Our product is guaranteed to satisfy the following goals by the time for the final demo.
\begin{enumerate}
    \item Accurately identify which actors appear in a movie clip with a high degree of certainty. The application will use face recognition to.
	\item Accurately identify what movie is playing by providing top guesses with confidence levels. We want our application to be able to identify all movies with a high degree of certainty.
	\item We want our application to identify the movie as quickly as possible with very little latency. By emulating real-time processing, the user gets results quickly in order to provide convenience.
	\item We want the interface to be friendly and easy to use for any type of user. Movies are popular with audiences of diverse ages so we want to make it easy for any movie-watchers.
\end{enumerate}

% End Section

\end{document}
%------------------------------------------------------------------------------