\documentclass[12pt, titlepage]{article}

% Imported Packages
%------------------------------------------------------------------------------
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{extarrows}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage[round]{natbib}
\usepackage{hyperref}
\usepackage{soul}

%------------------------------------------------------------------------------

% Header and Footer
%------------------------------------------------------------------------------
\pagestyle{plain}  
\renewcommand\headrulewidth{0.4pt}                          
\renewcommand\footrulewidth{0.4pt}                                    
%------------------------------------------------------------------------------

% Title Details
%------------------------------------------------------------------------------
\title{SE 4GB6: Project Goals\\ The Cut}
\author{Group 17
		\\ Joseph Lu - luy89
		\\ Matthew Po - pom
		\\ Stanley Liu - liuz23
		\\ Suhavi Sandhu - sandhs11
}
\date{October 7, 2019}                            
%------------------------------------------------------------------------------

% Document
%------------------------------------------------------------------------------
\begin{document}

\maketitle	
\newpage

\section{Project Goals}
\label{sec:project_goals}
% Begin Section

\subsection{Purpose}
\label{sub:purpose}
% Begin SubSection
    The purpose of this document is to identify project goals for \textbf{The Cut}, identifying the main components that will be developed. The intended audience for this document includes the stakeholders who comprise of Dr. Alan Wassyng, the developers Joseph Lu, Suhavi Sandhu, Matthew Po, and Stanley Liu, as well as the teaching assistants.
% End SubSection

\subsection{Project Deliverable}
\label{sub:system_description}
% Begin SubSection

 The Cut is an application that can identify movies based on movie clips. The application will return the movie title along with other metadata (cast, synopsis, genre, box office details, production company, etc) related to the film.

% End SubSection

\subsection{Main Goals}
\label{sub:main_goals}
% Begin SubSection

This section outlines the goals that we are aiming to achieve.
	
\begin{enumerate}
    \item Accurately identify which actors appear in a movie clip with a high degree of certainty. The application will use face recognition to.
	\item Accurately identify what movie is playing by providing top guesses with confidence levels. We want our application to be able to identify all movies with a high degree of certainty.
\end{enumerate}

\subsection{Secondary Goals}
\label{sub:secondary_goals}
% Begin SubSection

This section outlines the goals that will bring added quality/innovation/excitement to our product.

	
\begin{enumerate}
    \item The application will be able to identify foreign movies along with mainstream films to reach a wider audience. 
	\item The application will provide the metadata of the movie that has been identified such as cast members, synopsis, genre, box office details, production company, etc.
	\item We want our application to identify the movie as quickly as possible with very little latency. By emulating real-time processing, the user gets results quickly in order to provide convenience.
	\item We want the interface to be friendly and easy to use for any type of user. Movies are popular with audiences of diverse ages so we want to make it easy for any movie-watchers.
\end{enumerate}

% End Section

\end{document}
%------------------------------------------------------------------------------